An essentially algebraic formulation of dependent type theory

### 2015-02-10 Rules/rules_setup.tex
rewrite definition of valid inference rules

@@

The theory of contexts, families and terms shall be described by means of a
declaration of valid inference rules. An inference rule is an expression of the
form
\begin{equation*}
\inference{\mathcal{H}_1\quad\cdots\quad\mathcal{H}_n}{\mathcal{J}}
\end{equation*}
where each of $\mathcal{H}_1$, ..., $\mathcal{H}_n$ and $\mathcal{J}$ is 
judgment. The judgments $\mathcal{H}_1$, ..., $\mathcal{H}_n$ are called the
hypotheses and the judgment $\mathcal{J}$ is the conclusion of the inference
rule. When a judgment is the conclusion of a valid inference rule, we also say
that the judgment is valid or well-formed. In fact, the only way to construct
new judgments is via the valid inference rules we describe in this section.

The class of valid inference rules is closed under composition and under
rearranging the hypotheses. That
means that if
\begin{equation*}
\inference{\mathcal{I}_{1k}\quad\cdots\quad\mathcal{I}_{m_kk}}{\mathcal{H}_k}
\end{equation*}
and
\begin{equation*}
\inference{\mathcal{H}_1\quad\cdots\quad\mathcal{H}_n}{\mathcal{J}}
\end{equation*}
are valid inference rules for $1\leq k\leq n$, then
\begin{equation*}
\inference{\mathcal{I}_{11}\quad\cdots\quad\mathcal{I}_{m_11}\quad\cdots\quad\mathcal{I}_{1n}\quad\cdots\quad\mathcal{I}_{m_nn}}{\mathcal{J}}
\end{equation*}
is also a valid inference rule. Also, in a valid inference rule 
duplicated hypotheses may always be contracted and hypotheses may always be 
reordered; the result is still considered a valid inference rule.

>>>>

The theory of contexts, families and terms shall be described by means of a
declaration of valid inference rules. An inference rule is a finite list
$\mathcal{H}_1,\ldots,\mathcal{H}_n;\mathcal{J}$ of expressions called
judgments. Usually we represent an inference rule in the following
form
\begin{equation*}
\inference{\mathcal{H}_1\quad\cdots\quad\mathcal{H}_n}{\mathcal{J}}
\end{equation*}
The judgments $\mathcal{H}_1$, \ldots, $\mathcal{H}_n$ are called the
hypotheses and the judgment $\mathcal{J}$ is the conclusion of the inference
rule.

\begin{defn}
An inference rule is called \emph{valid} in either of the following cases:
\begin{itemize}
\item It is declared valid as an axiom;
\item The inference rule
\begin{equation*}
\inference{\mathcal{H}_1\quad\cdots\quad\mathcal{H}_n}{\mathcal{H}_n}
\end{equation*}
is a valid inference rule;
\item If
\begin{equation*}
\inference{\mathcal{I}_{1k}\quad\cdots\quad\mathcal{I}_{m_kk}}{\mathcal{H}_k}
\end{equation*}
and
\begin{equation*}
\inference{\mathcal{H}_1\quad\cdots\quad\mathcal{H}_n}{\mathcal{J}}
\end{equation*}
are valid inference rules for $1\leq k\leq n$, then
\begin{equation*}
\inference{\mathcal{I}_{11}\quad\cdots\quad\mathcal{I}_{m_11}\quad\cdots\quad\mathcal{I}_{1n}\quad\cdots\quad\mathcal{I}_{m_nn}}{\mathcal{J}}
\end{equation*}
is also a valid inference rule.
\item If
\begin{equation*}
\inference{\mathcal{H}_1\quad\cdots\quad\mathcal{H}_n}{\mathcal{H}_{n+1}}
\qquad
\text{and}
\qquad
\inference{\mathcal{H}_1\quad\cdots\quad\mathcal{H}_{n+m+1}}{\mathcal{J}}
\end{equation*}
are valid inference rules, then
\begin{equation*}
\inference{\mathcal{H}_1\quad\cdots\quad\hat{\mathcal{H}}_{n+1}\quad\cdots\quad\mathcal{H}_{n+m+1}}{\mathcal{J}}
\end{equation*}
where the hypothesis $\mathcal{H}_{n+1}$ is omitted, is a valid inference rule.
\end{itemize}
\end{defn}

@@
